---
title: "Q3: How are the 'best' models affected by important characteristics of stand structure, that are NOT easily attainable?"
output: html_document
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figs-knitr-3/",
  cache.path = "cache-3/",
  cache = TRUE,
  autodep = TRUE
)
```

We'll start by loading some packages and reading in a number of functions that
are included in `zoib-functions.R`:

```{r functions, cache=FALSE, warning=FALSE, message=FALSE, results='hide'}
library(here)
source(here("analysis/zoib-functions.R"))
library("ggplot2")
library("dplyr")
library("rstan")
library("readr")
library("doParallel")
library("forcats")
library("ggsidekick") # devtools::install_github("seananderson/ggsidekick")
rstan_options(auto_write = TRUE)
options(mc.cores = 1)
sm <- stan_model(here("analysis/zoib1re.stan"))
sm_oib <- stan_model(here("analysis/oib1re.stan"))
registerDoParallel(cores = round(parallel::detectCores()))
iter <- 1000L
chains <- 4L
file <- here("data", "BurnSeverity.csv")

var_names <- read.csv(here("data/VariableNames.csv"), 
  stringsAsFactors = FALSE, strip.white = TRUE) %>%
  rename(y = old.names)
response_order <- c(
  "Basal area killed by fire",
  "Trees killed by fire",
  "Bole scorch",
  "Char height",
  "Charred surface cover"
)
thresholds <- seq(0.05, 0.95, length.out = 5)
quants <- c(0.05, 0.5, 0.95)
.cols <- viridis::plasma(3, end = 0.85) %>% rev()
```

Because the quadratic mean diameter predictors are not available for the 0s (not
burned at all) we will have to use a "OIB" one-inflated-beta GLMM. Here I am
including all of the interactions in a single model. Note that each predictor
has been scaled by dividing by 2 SDs and subtracting its mean. This puts them on
approximately the same scale.

```{r q3-fit, cache=TRUE}
x_vars <- c(
  "RdNBR_BL",
  "RdNBR_BL",
  "RdNBR_BL",
  "RdNBR_BL",
  "RdNBR_BL"
)
y_vars <- c(
  "BOLESCORCH",
  "CHARCOV",
  "CHARHT_percMax",
  "Firemort.BA.p",
  "Firemort.trees.p"
)
vars <- data.frame(x = x_vars, y = y_vars, stringsAsFactors = FALSE)

x_vars <- tolower(c("xscaled"))
extra_x_vars <- c("qmd_all", "ba_ha", "stems_ha", "redgraygreenstage_ba_p")
x_vars <- paste(x_vars, extra_x_vars, sep = " * ")

out_q3 <- plyr::mlply(.data = vars, function(x, y) { # or map2() without parallel
  d <- get_dat(!!quo_name(y), !!quo_name(x), file = file, max_predictor = 2500)
  dd <- filter(d, !is.na(qmd_all))
  m <- fit_model_oib(dd, sm_oib,
    predictors = x_vars, iter = iter, chains = chains, cores = 1
  )
  list(m = m, d = dd, x = x, y = y)
}, .parallel = TRUE)
```

Let's plot out the main effect coefficients and the interaction coefficients.
This takes a little bit of data manipulation first. The dots are medians, the
thick lines are 50% credible intervals, and the thin lines are 95% credible
intervals.

```{r plot-interactions, cache=TRUE, fig.height=9, fig.width=10}
out_q3_plot <- out_q3

for (i in seq_along(out_q3_plot)) {
  out_q3_plot[[i]]$y <- var_names$new.names[var_names$y == out_q3_plot[[i]]$y]
}

newnames_df <- data.frame(
  name = c(
    " RdNBR_BL", "qmd_all", "ba_ha", "stems_ha", "redgraygreenstage_ba_p",
    " RdNBR_BL:qmd_all", " RdNBR_BL:ba_ha", " RdNBR_BL:stems_ha",
    " RdNBR_BL:redgraygreenstage_ba_p"
  ),
  new.names = c(
    " RdNBR", "QMD", "Stand basal area", "Stand density", "Pre-fire beetle outbreak severity",
    " RdNBR x QMD", " RdNBR x stand basal area", " RdNBR x stand density",
    " RdNBR x pre-fire beetle outbreak severity"
  ),
  stringsAsFactors = FALSE
)

p_q3 <- lapply(out_q3_plot, function(x)
  plot_zoib_coefs(x, oib = TRUE, newnames_df = newnames_df, return_df = TRUE))
p_q3 <- bind_rows(p_q3)
pal <- RColorBrewer::brewer.pal(3, "Set2")
x_name <- " RdNBR"
p_q3 <- mutate(p_q3, xvar = fct_relevel(name, x_name, after = Inf))
p_q3 <- mutate(p_q3, response = factor(response, levels = response_order))

gg <- ggplot(p_q3, aes(
  y = estimate, x = xvar,
  colour = model_full, shape = interaction
)) +
  geom_hline(yintercept = 0, lty = 2, col = "grey55") +
  geom_linerange(aes(ymin = conf.low.25, ymax = conf.high.75),
    position = position_dodge(width = 0.4), size = 0.85
  ) +
  geom_linerange(aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(width = 0.4), size = 0.35
  ) +
  geom_point(position = position_dodge(width = 0.4), size = 1.8) +
  xlab("") +
  facet_wrap(~response) +
  ggsidekick::theme_sleek() +
  coord_flip() +
  scale_color_manual(values = pal, guide = guide_legend(reverse = TRUE)) +
  scale_shape_manual(values = c(19, 21)) +
  labs(colour = "Model", shape = "Interaction", y = "Coefficient value") +
  guides(shape = FALSE) +
  theme(legend.position = c(0.8, 0.3))

ggsave(here("analysis/figs/q3-coefs-facets.pdf"), width = 7.2, height = 5.4)
```

```{r}
inter_vars <- c("qmd_all", "ba_ha", "stems_ha", "redgraygreenstage_ba_p")
inter_vars_long <- c(
  "QMD", "Stand\nbasal area", "Stand density",
  "Pre-fire beetle\noutbreak severity"
)
vars_i <- seq_along(inter_vars)
response_j <- seq_along(out_q3)
q3_inter_plots <- list()
k <- 0
for (j in response_j) {
  for (i in vars_i) {
    k <- k + 1
    q3_inter_plots[[k]] <-
      plot_interaction(out_q3[[j]],
        int_var = inter_vars[i],
        int_lab = paste0("\n", inter_vars_long[i]),
        xlab = gsub("_BL", "", "RdNBR_BL"), col = .cols, .quant = quants,
        title = var_names$new.names[var_names$y == vars$y[[j]]],
        type = "oib", return_data = TRUE
      )
    q3_inter_plots[[k]]$interaction <- inter_vars_long[i]
    q3_inter_plots[[k]]$response <- var_names$new.names[var_names$y == vars$y[[j]]]
  }
}
q3_inter_plots_df <- bind_rows(q3_inter_plots)
q3_inter_plots_df$level <- as.factor(q3_inter_plots_df$level)

dd <- get_dat(
  response = "Firemort.BA.p",
  main_predictor = "RdNBR_BL", file = file
)

lets <- expand.grid(
  response = factor(response_order, levels = response_order),
  interaction = factor(inter_vars_long, levels = sort(inter_vars_long))
) %>%
  arrange(interaction, response) %>%
  mutate(panel = paste0("(", letters[seq_len(n())], ")"))

xlim_range <- range(dd$x)
g <- ggplot(q3_inter_plots_df, aes(x, est,
  ymin = lwr, ymax = upr,
  group = level, fill = level
)) +
  geom_line(lwd = 1.2, aes(colour = level)) +
  geom_ribbon(alpha = 0.25) +
  facet_grid(interaction ~ factor(response, levels = response_order)) +
  ggsidekick::theme_sleek() +
  ylab("Proportion") +
  labs(
    colour = "Quantile",
    fill = "Quantile"
  ) +
  scale_colour_manual(values = .cols, guide = guide_legend(reverse = TRUE)) +
  scale_fill_manual(values = .cols, guide = guide_legend(reverse = TRUE)) +
  scale_y_continuous(breaks = c(seq(0, 0.8, 0.2)), limits = c(0, 1)) +
  coord_cartesian(expand = FALSE) +
  theme(
    legend.justification = c(1, 0), legend.position = c(0.2, 0.8),
    panel.spacing = unit(-0.05, "lines"),
    legend.title = element_text(size = rel(0.8))
  ) +
  xlab("RdNBR") +
  xlim(xlim_range) +
  geom_text(
    data = lets, aes(label = panel), x = -100, y = 0.9,
    inherit.aes = FALSE, col = "grey30"
  )

pdf(here("analysis/figs/q3-interaction-ribbons.pdf"), width = 8, height = 5.5)
print(g)
dev.off()
```
